Carbonate chemistry at Ny-Ålesund

### 2023-03-01 awipev-CO2.Rmd

# ```{r make location map}
# svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
#         legends = FALSE, glaciers = FALSE)
# ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
# kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
#         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
# ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
# ```

>>>>

```{r make location map}
# svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
#         legends = FALSE, glaciers = FALSE)
# ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
# kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
#         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
# ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
# ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
```
